---
title: "Fid_Nov_18"
author: "Weiling Li"
date: "11/18/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE)
pacman::p_load(pracma,lubridate,tidyverse,corrplot,arm,readxl,coin)
``` 
```{r source equation, echo = TRUE}
## reads in functions that calculate daily log returns, log closed value, etc.
source(file = "./functions/fid_data_wrangler.R")
## reads in functions calculate goodness of fit
source(file = "./functions/fid_goodness_of_fit.R")
```

```{r set start date}
## restrict ourselves to study data after 2014-01-01
StartDate = as.Date("2014-01-01")

```

```{r Load Data, echo=TRUE}
FSPTX = dailynlogReturn(StartDate,read_csv("./Index_Data/FSPTX.csv"))      ## Target Fund
NASDAQ = dailynlogReturn(StartDate,read_csv("./Index_Data/^IXIC.csv"))     ## NASDAQ
SnP500 = dailynlogReturn(StartDate,read_csv("./Index_Data/^GSPC.csv"))     ## S&P500
SnPMID = dailynlogReturn(StartDate,read_csv("./Index_Data/^MID.csv"))      ##
SnPSML = dailynlogReturn(StartDate,read_csv("./Index_Data/^SML.csv"))
RUSSELL2000 = dailynlogReturn(StartDate,read_csv("./Index_Data/^RUT.csv"))
VGT = dailynlogReturn(StartDate,read_csv("./Index_Data/VGT.csv"))
VIGAX = dailynlogReturn(StartDate,read_csv("./Index_Data/VIGAX.csv"))
VTSAX = dailynlogReturn(StartDate,read_csv("./Index_Data/VTSAX.csv"))
SnP500Info <- dailynlogReturn(StartDate,read_csv("./Index_Data/SnP500Info.csv"))
SnPNATech <- dailynlogReturn(StartDate,read_csv("./Index_Data/SnPNATECH_clean.csv"))
MSCI_INFO_TECH <- dailynlogReturn(StartDate,read_xls(path = "./Index_Data/MSCI_Us_IMI_information_Tech_25-50_Index.xls",sheet = 1,col_names = c("Date","Close"),skip = 1))
Benchmark_industry_XOI <- dailynlogReturn(StartDate,read_csv("Index_Data/Benchmark_industry_XOI.csv"))
VIX <- dailynlogReturn(StartDate,read_csv("./Index_Data/^VIX.csv"))
```

```{r clean benchmark data: MSCI Info Tech}
## The Original Date in MSCI table is in datetime format, need to convert into date format
MSCI_INFO_TECH <- MSCI_INFO_TECH%>%dplyr::mutate(`Date` = as_date(Date))
MSCI_INFO_TECH <- dplyr::left_join(FSPTX%>%dplyr::select(Date),MSCI_INFO_TECH)

```

```{r filter dividen dates}
## This part is from previous EDA, Too lazy to rewrite things
dailyReturnComp = cbind(as.Date(FSPTX$Date),FSPTX$dailyReturn,NASDAQ$dailyReturn,SnP500$dailyReturn,VGT$dailyReturn,VIGAX$dailyReturn,VTSAX$dailyReturn)
colnames(dailyReturnComp) = c("Date","FSPTX","NASDAQ","SnP500","VGT","VIGAX","VTSAX")
epsilon = 0.000000000000000001
dailyReturnComp = data.frame(dailyReturnComp)%>%mutate(Date = as_date(Date),vsNASDAQ = ifelse(NASDAQ*NASDAQ<=epsilon,FSPTX,FSPTX/NASDAQ),vsSnP500 = ifelse(SnP500*SnP500<=epsilon,FSPTX,FSPTX/SnP500),vsVGT = ifelse(VGT*VGT<=epsilon,FSPTX,FSPTX/VGT),vsVIGAX = ifelse(VIGAX*VIGAX<=epsilon,FSPTX,FSPTX/VIGAX),vsVTSAX = ifelse(VTSAX*VTSAX<=epsilon,FSPTX,FSPTX/VTSAX))%>%mutate(minusNASDAQ = FSPTX-NASDAQ,minusSnP500 = FSPTX-SnP500,minusVGT = FSPTX-VGT,minusVIGAX= FSPTX-VIGAX,minusVTSAX = FSPTX-VTSAX)

## Capture Dividen dates
DividenDates <- dailyReturnComp%>%dplyr::filter(minusNASDAQ < -0.025)%>%dplyr::select(Date)%>%pull()
## Drop the dates from all indexes
FSPTX <-  FSPTX%>%dplyr::filter(!Date %in% DividenDates)
NASDAQ  <- NASDAQ%>%dplyr::filter(!Date %in% DividenDates)
SnP500  <- SnP500%>%dplyr::filter(!Date %in% DividenDates)
SnPMID <- SnPMID%>%dplyr::filter(!Date %in% DividenDates)
SnPSML  <- SnPSML%>%dplyr::filter(!Date %in% DividenDates)
RUSSELL2000  <- RUSSELL2000%>%dplyr::filter(!Date %in% DividenDates)
VGT  <- VGT%>%dplyr::filter(!Date %in% DividenDates)
VIGAX  <- VIGAX%>%dplyr::filter(!Date %in% DividenDates)
VTSAX  <- VTSAX%>%dplyr::filter(!Date %in% DividenDates)
SnP500Info <- SnP500Info%>%dplyr::filter(!Date %in% DividenDates)
SnPNATech <- SnPNATech%>%dplyr::filter(!Date %in% DividenDates)
MSCI_INFO_TECH <- MSCI_INFO_TECH%>%dplyr::filter(!Date %in% DividenDates)
Benchmark_industry_XOI <- Benchmark_industry_XOI%>%dplyr::filter(!Date %in% DividenDates)
VIX <- VIX%>%dplyr::filter(!Date %in% DividenDates)

## Get the dates and store them for indicator usage.
dates <- FSPTX%>%dplyr::select(Date)%>%dplyr::mutate(Year = format.Date(Date,"%Y"))

```

```{r Indicators: Hightech Export by percentage by year}

hightech.expo <- read_xls("./Indicators/HighTechExportsPercentage.xls",skip = 3,col_names = TRUE,sheet = 1)%>%  # Read data
  dplyr::select(1:2,`2007`:`2018`)%>%  #select years interested
  # main focus is United States
  dplyr::filter(`Country Code` %in% c("USA"))%>%
  # Rearrange the table so that it can be left_join to the dates table
  tidyr::pivot_longer(cols = `2007`:`2018`,names_to = "Year",values_to = "expo.perc")
```

```{r Overall Indicators for backup}
all.indicators <- read.csv("./Indicators/MainSci&Tech.csv",header = TRUE)%>%dplyr::filter(COU %in% "USA")
```

```{r Researchers in R&D per million population}
rnd.permil <- read_xls("./Indicators/ResearchersinR&D.xls",skip = 3,col_names = TRUE,sheet = 1)%>%
  dplyr::select(1:2,`1996`:`2018`)%>%
  dplyr::filter(`Country Code` %in% c("USA"))%>%
  tidyr::pivot_longer(cols = `1996`:`2018`,names_to = "Year",values_to = "R&DperMil")
```

```{r Scientific and Technology Journals indicator}
SciJour.indicator <- read_xls("./Indicators/ScientificJournalIndicator.xls",skip = 3,col_names = TRUE,sheet = 1)%>%
  dplyr::select(1:2,`2013`:`2018`)%>%
  dplyr::filter(`Country Code` %in% c("USA"))%>%
  tidyr::pivot_longer(cols = `2013`:`2018`,names_to = "Year",values_to = "Sci.Jour")
```

```{r Trademark Application per year}
Trademarkappli.peryear <- read_xls("./Indicators/TradeMarkApplication.xls",skip = 3,col_names = TRUE,sheet = 1)%>%
  dplyr::select(1:2,`1980`:`2018`)%>%
  dplyr::filter(`Country Code` %in% c("USA"))%>%
  tidyr::pivot_longer(cols = `1980`:`2018`,names_to = "Year",values_to = "Trademark.appl")
```

## fit benchmark

The logic goes:

* fit a `lm` model with `FSPTX` as the outcome and benchmark(`MSCI US IMI Info Tech 25/50`) as predictor(drop intercept)

* Check if fund and benchmark has linear relationship

* Check residuals
  - Does the residual plot show any trend?
  - Is residual follows a normal distribution?
  - Standardized residual Show follows a distribution of $\mathcal{N}(0,1)$. Does the residual plot support that?
  
* Check if we can regenerate the original data
  - Calculate $y_{sim}$ and $y_{obs}$.
  - KS test: Check if we can reject the hypothesis they are from the same distribution.
  - Permutation test: Check if we can reject the hypothesis that they are independent.
  - T test: If they are dependent, check the mean of them using t test.(assume normality)
  - F test: If they are dependent, check the if the variance are different using f test.(assume normality)
  - Visually compare results using histogram.

```{r fit benchmark and fit check, echo = TRUE}


ggplot()+aes(x = FSPTX$log.Return, y = MSCI_INFO_TECH$log.Return)+
  geom_point()+xlab("FSPTX")+ylab("MSCI IT")+ggtitle(label = "Check linear relationship")

fit.benchmark <- lm(FSPTX$log.Return~MSCI_INFO_TECH$log.Return-1)
summary(fit.benchmark)

p.benchmark <- plotmodel(fit.benchmark,"y ~ MSCI(benchmark) - 1","#CE8891")
## check residuals
p.benchmark$redisualplot
p.benchmark$qqplot
## check standardized residuals the 95% interval
quantile(scale(fit.benchmark$residuals),probs = c(.25,.95))
## simulate fake data and compare results
md_test(fit.benchmark,method = "pearson",modelequation ="y ~ MSCI(benchmark) - 1" )

```